\subsection{Proofs of progress and termination}
Our refinement strategy ensures progress, i.e., the spurious counterexample does not
repeat in the future
iterations of Algorithm~\ref{algo:main}. Let us suppose the algorithm
$\textsc{getMarkedNeurons}$ gets the abstract spurious counterexample
${v_0}, {v_1}, ... {v_k}$ and
returns marked neurons in $i$th iteration.
The call to $\maxsat{}$ at line 10
declares that $constr \land softsatSet$ is satisfiable.
We can extract an abstract spurious counterexample from a model
of $constr \land softsatSet$.
Let $m$ be the model.
Let the abstract spurious counterexample be $cex = val_0^{v_0}, ...., val^{v_0}_{i-1},v'_{i},...,v'_{k-1},v_k$.
Before the step $i$, $cex$ follows the execution of $N$ on input $v_0$.
After the step $i$, we use the model to construct $cex$, i.e., $m(x_i) = v'_i$.

\begin{theorem}
  In the rest of the run of Algorithm~\ref{algo:main}, we will never find the abstract
  spurious counterexample
  $cex$ again.
\end{theorem}
\begin{proof}
  For $n_{ij} \in newMarked$, the \maxsat{} query ensures that
  $val^{v_0}_{ij} \neq v'_{ij}$.
  If we have the same counterexample again in the future then
  input of $n_{ij}$ will be $val^{v_0}_{(i-1)j}$.
  Since we will have exact encoding for $n_{ij}$, the output
  will be $val^{v_0}_{ij}$, which contradicts the earlier inequality.  
\end{proof}

Further, we prove that our method always terminates.
%
Theorems \ref{th:progress1} and \ref{th:progress2} imply that in every
iteration $\textsc{getMarkedNeurons}$
returns a nonempty set of unmarked neurons, which we will now be marked. In worst case the algorithm marked all 
the neurons of the network, and encode them in the exact behavior. 

% Suppose the algorithm {\em getMarkedNeurons} get abstractCEX 
% ${v_0}, {v_1}, ... {v_k}$ as input, 
% and ${val_i^{{v_0}}}$ represents the value vector on layer $l_i$, 
% when we execute the neural network on input ${v_0}$.




\begin{theorem}
  \label{th:progress1}
  In every refinement iteration $\textsc{getMarkedNeurons}$
  returns a non-empty set of marked neurons. 
\end{theorem}

\begin{proof}
By the definition of abstract spurious counterexample, ${v_k} \models \lnot Q$. 
By the check at line 6 of Algorithm~\ref{algo:main} ${val_k^{{v_0}}} \models Q$. 
If the set of returned new marked neurons is empty, $newMarked = \emptyset$ for each layer. 
Therefore, all the neurons in any layer $l_i$ become equal to ${val_i^{{v_0}}}$,  
which implies ${v_k}$ equals to ${val_k^{{v_0}}}$, but ${v_k} \models \lnot Q$ and 
${val_k^{{v_0}}} \models Q$, which is a contradiction.   
\end{proof}
% {\em Proof by contradiction:} 


\begin{theorem}
  \label{th:progress2}
  In every refinement iteration $\textsc{getMarkedNeurons}$
  returns marked neurons, which were not marked in previous iterations. 
\end{theorem}

\begin{proof}
We will show that if a neuron $n_{ij}$ got marked in $t^{th}$ iteration then $n_{ij}$ will not be marked again in any iteration greater than $t$.
Consider an iteration $t' > t$, if we get the marked neurons from layer other
than $l_i$ then $n_{ij}$ can not be part of it because $n_{ij}$ is in layer $l_i$. 
Consider the case where marked neurons are from the layer $l_i$ in $t'^{th}$ iteration. 
Since we have made $n_{ij}$ exact in line 6 of Algorithm~\ref{algo:refine2},
its behavior while optimizing constraints will be same as the exact \relu{}. 
Moreover, $v'_{ij} = val_{ij}^{v_0}$, 
which implies the soft constraint for neuron $n_{ij}$ will always be satisfied. Hence it will not occur as a marked neuron as per the criteria of marked neurons in line 11 of Algorithm~\ref{algo:refine2}.   \todo{check last line.}
\end{proof}


%%% Local Variables:
%%% mode: latex
%%% TeX-master: "../main"
%%% End:
